---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  font-family: Arial, sans-serif;
  max-width: 800px;
  margin: auto;
  padding: 20px;
  background-color: #f9f9f9;
}

h2 {
  color: #2c3e50;
  border-bottom: 2px solid #3498db;
  padding-bottom: 8px;
}

p {
  color: #333;
  line-height: 1.6;
}
```

## Public Transport Observation Log

This report tracks public transport observations collected over a two-week period in Auckland.Data was logged each time a bus or train/metro was taken, recording the time period, crowding level, wait time, and seat availability.

```{r}
library(tidyverse)

logged_data <- read_csv(
  "https://docs.google.com/spreadsheets/d/e/2PACX-1vRvqi0IotSPUo7aiex_mhzWuy8b09tx3_Tquu4-AZSZi4ksNMYq1Y35POF04gnNvctUTpRFDhOdSWBf/pub?gid=2082785426&single=true&output=csv"
)

latest_data <- logged_data %>%
  rename(
    timestamp   = Timestamp,
    transport   = `What type of transport did you take?`,
    time_period = `What time period did you travel?`,
    crowded     = `How crowded was the vehicle?`,
    wait_time   = `How many minutes did you wait for the transport?`,
    seats_full  = `Were the seats full?`
  )

mean_wait      <- round(mean(latest_data$wait_time, na.rm = TRUE), 1)
max_wait       <- max(latest_data$wait_time, na.rm = TRUE)
total_obs      <- nrow(latest_data)
busiest_period <- latest_data %>%
  count(time_period) %>%
  slice_max(n, n = 1) %>%
  pull(time_period)
```

A total of `r total_obs` trips were recorded. The average waiting time was `r mean_wait` minutes, with the longest wait being `r max_wait` minutes. The busiest travel period was the `r busiest_period[1]`.
```{r}
ggplot(latest_data, aes(x = time_period)) +
  geom_bar(fill = "steelblue") +
  labs(
    title = "Number of Trips by Time Period",
    x = "Time Period",
    y = "Count"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 15, hjust = 1))
```
```{r}
ggplot(latest_data, aes(x = crowded)) +
  geom_bar(fill = "coral") +
  labs(
    title = "Distribution of Crowding Levels",
    x = "Crowding Level",
    y = "Count"
  ) +
  theme_minimal()
```
